Fourmile Calibrations and Output

### 2025-05-09 fourmile_output_dec2024.Rmd
added flow partition summary

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD1_w), size =1) +
  facet_wrap(~year, scales="free", ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD1') +
  theme(text = element_text(size = 20)) +
  labs(y = 'RD1 (mm)') +
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD2') +
  theme(text = element_text(size = 20))+
  labs(y = 'RD2 (mm)')+
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG1') +
  theme(text = element_text(size = 20)) +
  labs(y = 'RG1 (mm)')+
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG2') +
  theme(text = element_text(size = 20))+
  labs(y = 'RG2 (mm)')+
  theme_bw(base_size=20)

@@

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD1 (mm)') +
  theme(text = element_text(size = 20)) +
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum), size = 1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD2 (mm)') +
  theme(text = element_text(size = 20))+
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum), size  = 1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG1 (mm)') +
  theme(text = element_text(size = 20))+
  theme_bw(base_size=20)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG2 (mm)') +
  theme(text = element_text(size = 20))+
  theme_bw(base_size=20)

@@

>>>>

# ggplot(gw, aes(x=date, color = source)) +
#   geom_line(aes(y=catchmentRD1_w), size =1) +
#   facet_wrap(~year, scales="free", ncol = 2) +
#   scale_x_date(labels = date_format("%b")) +
#   ggtitle('RD1') +
#   theme(text = element_text(size = 20)) +
#   labs(y = 'RD1 (mm)') +
#   theme_bw(base_size=20)
# 
# ggplot(gw, aes(x=date, color = source)) +
#   geom_line(aes(y=catchmentRD2_w), size =1) +
#   facet_wrap(~year, scales = 'free', ncol = 2) +
#   scale_x_date(labels = date_format("%b")) +
#   ggtitle('RD2') +
#   theme(text = element_text(size = 20))+
#   labs(y = 'RD2 (mm)')+
#   theme_bw(base_size=20)
# 
# ggplot(gw, aes(x=date, color = source)) +
#   geom_line(aes(y=catchmentRG1_w), size =1) +
#   facet_wrap(~year, scales = 'free', ncol = 2) +
#   scale_x_date(labels = date_format("%b")) +
#   ggtitle('RG1') +
#   theme(text = element_text(size = 20)) +
#   labs(y = 'RG1 (mm)')+
#   theme_bw(base_size=20)
# 
# ggplot(gw, aes(x=date, color = source)) +
#   geom_line(aes(y=catchmentRG2_w), size =1) +
#   facet_wrap(~year, scales = 'free', ncol=2) +
#   scale_x_date(labels = date_format("%b")) +
#   ggtitle('RG2') +
#   theme(text = element_text(size = 20))+
#   labs(y = 'RG2 (mm)')+
#   theme_bw(base_size=20)

@@

# ggplot(gw, aes(x=date, color = source)) +
#   geom_line(aes(y=RD1cumsum), size =1) +
#   facet_wrap(~year, scales = 'free', ncol=2) +
#   scale_x_date(labels = date_format("%b")) +
#   ggtitle('Cumulative RD1 (mm)') +
#   theme(text = element_text(size = 20)) +
#   theme_bw(base_size=20)
# 
# ggplot(gw, aes(x=date, color = source)) +
#   geom_line(aes(y=RD2cumsum), size = 1) +
#   facet_wrap(~year, scales = 'free', ncol=2) +
#   scale_x_date(labels = date_format("%b")) +
#   ggtitle('Cumulative RD2 (mm)') +
#   theme(text = element_text(size = 20))+
#   theme_bw(base_size=20)
# 
# ggplot(gw, aes(x=date, color = source)) +
#   geom_line(aes(y=RG1cumsum), size  = 1) +
#   facet_wrap(~year, scales = 'free', ncol = 2) +
#   scale_x_date(labels = date_format("%b")) +
#   ggtitle('Cumulative RG1 (mm)') +
#   theme(text = element_text(size = 20))+
#   theme_bw(base_size=20)
# 
# ggplot(gw, aes(x=date, color = source)) +
#   geom_line(aes(y=RG2cumsum), size =1) +
#   facet_wrap(~year, scales = 'free', ncol = 2) +
#   scale_x_date(labels = date_format("%b")) +
#   ggtitle('Cumulative RG2 (mm)') +
#   theme(text = element_text(size = 20))+
#   theme_bw(base_size=20)

@@

flow_summ <- gw_maxcumsum %>%
  #filter(!year == 2013) %>%
  group_by(source, flow_type) %>%
  summarize(min = min(flow_cms),
            max = max(flow_cms))
